Recursive Solutions to \\First-Order Model Counting

### 2023-02-05 doc/talks/3_long/talk.tex
2/4 proofs complete (an overhaul of Preliminaries)

\usetikzlibrary{shapes}
\usetikzlibrary{arrows}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{positioning}
\usetikzlibrary{overlay-beamer-styles}
\usetikzlibrary{shapes.callouts}
\usetikzlibrary{cd}

@@

\definecolor{color1}{HTML}{1B9E77}
\definecolor{color2}{HTML}{D95F02}

@@

% 15 min introduction
% 20-25 min presentation
% 5-10 min summary
% 20-25 slides
% before it was 15 slides and 20 min
% TODO: use \alert instead of \structure
% TODO: replace capital latin letters with capital Greek letters

@@

\begin{frame}{What Computers Can and Cannot Do}
  \begin{tikzpicture}[remember picture,overlay]
    \node[right=0.7cm] at (current page.west) (stickman) {\includegraphics[height=0.5\textheight]{stickman.png}};
    \node<-4>[left,shift=({0, -2})] at (current page.east) (computer) {\includegraphics[height=0.5\textheight]{happy_computer}};
    \node<2>[ellipse callout, draw, right=0cm, callout relative pointer={(-1, -0.5)}] at (stickman.north east) {$\int_{-\infty}^{\infty} e^{-t^{2}}\,\mathrm{d}t$};
    \node<2>[ellipse callout, draw, left=-0.5cm, below=0.5cm] at (computer.north west) {$\sqrt{\pi}$};
    \node<3>[ellipse callout, draw, right=-1cm, callout relative pointer={(-2.5, -0.5)}] at (stickman.north east) {Produce a schedule for the nurses at NUH.};
    \node<3>[ellipse callout, draw, below=0.5cm, shift=({-0.5,0}), callout relative pointer={(0.5, -0.25)}] at (computer.north west) {\includegraphics[width=0.1\textwidth]{schedule}};
    \node<4>[ellipse callout, draw, right=0cm, callout relative pointer={(-1, -0.15)}] at (stickman.north east) {Describe this picture. \includegraphics[width=0.25\textwidth]{cat.jpg}};
    \node<4>[ellipse callout, draw, below=0.5cm, shift=({-0.5,0.5}), callout relative pointer={(0.5, -0.5)}] at (computer.north west) {It's a cat with its eyes closed.};
    \node<5>[ellipse callout, draw, right=0cm, callout relative pointer={(-1, -0.15)}, text width=5cm] at (stickman.north east) {If I shuffle a deck of \alert{$n$} cards, how many possible outcomes are there?};
    \node<5>[left,shift=({-1, -1})] at (current page.east) (computer2) {\includegraphics[height=0.5\textheight]{overheating_computer}};
    \node[shift=({1.3, 0.1})] at (current page.south west) {\tiny \color{lightgray}{Vector art by Vecteezy.com}};
  \end{tikzpicture}
\end{frame}
% TODO: replace cat with 'Generate a picture of a monkey with a funny hat'

\begin{frame}[fragile]{Many Ways to Count}
  \begin{center}
    \begin{tikzcd}
      \WMI{} & \WFOMI{} \\
      \#\SAT{}/\WMC{} & \WFOMC{} \\
      \AMC{}, \pbp{} & \SPPP{}
    \end{tikzcd}
  \end{center}
\end{frame}
% maybe mention #CSP and other non-SAT ways of counting

>>>>

\usetikzlibrary{shapes}
\usetikzlibrary{positioning}
\usetikzlibrary{overlay-beamer-styles}
\usetikzlibrary{shapes.callouts}
\usetikzlibrary{cd}
\usetikzlibrary{calc}

@@

\definecolor{color1}{HTML}{1B9E77}
\definecolor{color2}{HTML}{D95F02}
\definecolor{highlightcolor}{HTML}{22373A}

@@

% 15 min introduction
% 20-25 min presentation
% 5-10 min summary
% 20-25 slides
% before it was 15 slides and 20 min
% make sure there's a clear and coherent storyline
% TODO: use \alert instead of \structure
% TODO: replace capital latin letters with capital Greek letters
% TODO: add a very clear example of what a model is
% TODO: could add the step-by-step walkthrough of what FOKC looks like

@@

\begin{frame}{What Computers Can and Cannot Do}
  \begin{tikzpicture}[remember picture,overlay]
    \node[right=0.7cm] at (current page.west) (stickman) {\includegraphics[height=0.5\textheight]{stickman.png}};
    \node<-4>[left,shift=({0, -2})] at (current page.east) (computer) {\includegraphics[height=0.5\textheight]{happy_computer}};
    \node<2>[ellipse callout, draw, right=0cm, callout relative pointer={(-1, -0.5)}] at (stickman.north east) {$\int_{-\infty}^{\infty} e^{-t^{2}}\,\mathrm{d}t$};
    \node<2>[ellipse callout, draw, left=-0.5cm, below=0.5cm] at (computer.north west) {$\sqrt{\pi}$};
    \node<3>[ellipse callout, draw, right=-1cm, callout relative pointer={(-2.5, -0.5)}] at (stickman.north east) {Produce a schedule for the nurses at NUH.};
    \node<3>[ellipse callout, draw, below=0.5cm, shift=({-0.5,0}), callout relative pointer={(0.5, -0.25)}] at (computer.north west) {\includegraphics[width=0.1\textwidth]{schedule}};
    \node<4>[ellipse callout, draw, right=0cm, callout relative pointer={(-1, -0.15)}] at (stickman.north east) {Describe this picture. \includegraphics[width=0.25\textwidth]{cat.jpg}};
    \node<4>[ellipse callout, draw, below=0.5cm, shift=({-0.5,0.5}), callout relative pointer={(0.5, -0.5)}] at (computer.north west) {It's a cat with its eyes closed.};
    \node<5>[ellipse callout, draw, right=0cm, callout relative pointer={(-1, -0.15)}, text width=5cm] at (stickman.north east) {If I shuffle a deck of \alert{$n$} cards, how many possible outcomes are there?};
    \node<5>[left,shift=({-1, -1})] at (current page.east) (computer2) {\includegraphics[height=0.5\textheight]{overheating_computer}};
    \node[shift=({1.3, 0.1})] at (current page.south west) {\tiny \color{lightgray}{Vector art by Vecteezy.com}};
  \end{tikzpicture}
\end{frame}
% TODO: replace cat with 'Generate a picture of a monkey with a funny hat' (make sure it's legal to use)

\begin{frame}[fragile]{There Are Many Ways to Count}
  \begin{center}
    \begin{tikzcd}[remember picture]
      |[alias=WMI]|\WMI{} & \WFOMI{} \\
      |[alias=WMC]|\#\SAT{}/\WMC{} \ar[u] \ar[d] \ar[r] & \WFOMC{} \ar[u] \ar[d] \\
      |[alias=PBP]|\AMC{}, \pbp{} & |[alias=SP]|\SPPP{}
    \end{tikzcd}
  \end{center}
  \begin{overprint}
    foo
  \end{overprint}
  \begin{tikzpicture}[overlay,remember picture]
    \begin{scope}[transform canvas={xshift=-3em}]
      \draw[->,draw=gray] ($(WMC)+(0,0.1)$)--($(WMI)+(0,0.5)$) node[midway,left] {\color{gray}{$\sum \to \int$}};
      \draw[->,draw=gray] ($(WMC)-(0,0.1)$)--($(PBP)-(0,0.5)$) node[midway,left] {\color{gray}{Generalising weights}};
    \end{scope}
    \begin{scope}[transform canvas={yshift=-2em}]
      \draw[->,draw=gray] ($(PBP)-(1,0)$)--($(SP)+(1,0)$) node[midway,below] {\color{gray}{From propositional to first-order logic}};
    \end{scope}
  \end{tikzpicture}
\end{frame}
% maybe mention #CSP and other non-SAT ways of counting (SMT?, counting paths in automata and directed graphs)
% TODO: gradually reveal parts of this diagram (1. axes + #SAT + WMC, 2. extension to FOL (with bottom label), 3. integration 4. bottom row)
% TODO: at the same time, show the full name and the reference for each at the bottom
% TODO: for future work, come back to this slide and add more arrows (e.g., beyond FOL)

% TODO: a big chunk of the introduction should provide motivation to my work (e.g., mention applications)
